### 2022-04-30 draft.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@03f82568b38b09780642ead845e1b8635034912d 🚀

%
Víctor Nicolás\,Velazco%
%
\,\textsuperscript{1}\quad %
\href{https://orcid.org/0000-0002-7911-4398}{Leonardo Ariel\,Saravia}%
%
\,\textsuperscript{2,3}

@@

Víctor Nicolás Velazco\textsuperscript{1,2}, Carlos Eduardo
Coviella\textsuperscript{1,2}, Liliana Beatriz
Falco\textsuperscript{1,2}, Leonardo Ariel Saravia\textsuperscript{3,4}

\textsuperscript{1} Departamento de Ciencias Básicas, Universidad
Nacional de Luján (Argentina), \textsuperscript{2} Instituto de Ecología
y Desarrollo Sustentable (UNLu -- CONICET), \textsuperscript{3}
Instituto de Ciencias, Universidad Nacional de General Sarmiento
(Argentina) \textsuperscript{4} Centro Austral de Investigaciones
Científicas (CADIC-CONICET), Ushuaia, Argentina.

Corresponding author:

Dr.~Leonardo A. Saravia

\underline{lsaravia@campus.ungs.edu.ar}

Universidad Nacional de General Sarmiento

J.M. Gutierrez 1159 (1613) Los Polvorines

Buenos Aires Argentina

Author contributions: LF and LS originally formulated the idea, NV, CC
developed the methodology, NV, CC, LF, and LS analyzed the data and
wrote the manuscript.

@@

\newpage

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

@@

\newpage

\begin{longtable}[]{@{}lcccccccccccccccccc@{}}
\caption{Breakdown of resources by Nested boxes represent the main orders of Acari and Collembola. In parentheses is the total number of taxa for the taxonomic category. Within the cells, the number of taxa associated with the trophic resource is shown. M: Mesostigmata, S: Sarcoptiformes, T: Trombidiformes, A: Arthropleona, N: Neelipleona, Sy: Symphypleona.}\\
\toprule
\textbf{Trophic Resource} & \multicolumn{6}{l}{FAMILY} & \multicolumn{6}{l}{GENERA} & \multicolumn{6}{l}{SPECIES} \\ \addlinespace
\midrule
\endhead
& \vtop{\hbox{\strut M}\hbox{\strut (34)}} &
\vtop{\hbox{\strut S}\hbox{\strut (82)}} &
\vtop{\hbox{\strut T}\hbox{\strut (32)}} &
\vtop{\hbox{\strut A}\hbox{\strut (9)}} &
\vtop{\hbox{\strut N}\hbox{\strut (1)}} &
\vtop{\hbox{\strut Sy}\hbox{\strut (3)}} &
\vtop{\hbox{\strut M}\hbox{\strut (89)}} &
\vtop{\hbox{\strut S}\hbox{\strut (157)}} &
\vtop{\hbox{\strut T}\hbox{\strut (28)}} &
\vtop{\hbox{\strut A}\hbox{\strut (58)}} &
\vtop{\hbox{\strut N}\hbox{\strut (2)}} &
\vtop{\hbox{\strut Sy}\hbox{\strut (10)}} &
\vtop{\hbox{\strut M}\hbox{\strut (136)}} &
\vtop{\hbox{\strut S}\hbox{\strut (264)}} &
\vtop{\hbox{\strut T}\hbox{\strut (22)}} &
\vtop{\hbox{\strut A}\hbox{\strut (155)}} &
\vtop{\hbox{\strut N}\hbox{\strut (1)}} &
\vtop{\hbox{\strut Sy}\hbox{\strut (13)}} \\ \addlinespace
\textbf{Saprophytic fungi} & 7 & 68 & 10 & 9 & 1 & 2 & 11 & 120 & 10 &
54 & 1 & 7 & 7 & 160 & 3 & 119 & 1 & 8 \\ \addlinespace
\textbf{Microfauna} & 32 & 26 & 23 & 8 & 0 & 0 & 80 & 40 & 4 & 33 & 0 &
0 & 106 & 47 & 0 & 39 & 0 & 0 \\ \addlinespace
\textbf{Bacteria} & 4 & 55 & 6 & 9 & 1 & 2 & 4 & 91 & 7 & 38 & 2 & 5 & 3
& 109 & 7 & 67 & 1 & 5 \\ \addlinespace
\textbf{Litter} & 0 & 43 & 0 & 8 & 1 & 3 & 0 & 79 & 0 & 35 & 1 & 6 & 0 &
124 & 0 & 59 & 1 & 5 \\ \addlinespace
\textbf{Mycorrhizal fungi} & 2 & 31 & 3 & 7 & 0 & 1 & 1 & 44 & 0 & 28 &
0 & 2 & 0 & 54 & 0 & 46 & 0 & 2 \\ \addlinespace
\textbf{Plant tissue} & 0 & 42 & 5 & 7 & 0 & 2 & 0 & 72 & 4 & 20 & 0 & 7
& 0 & 100 & 3 & 26 & 0 & 7 \\ \addlinespace
\textbf{Springtails} & 24 & 0 & 27 & 2 & 0 & 0 & 53 & 0 & 13 & 3 & 0 & 0
& 80 & 0 & 9 & 4 & 0 & 0 \\ \addlinespace
\textbf{Mites} & 21 & 0 & 26 & 1 & 0 & 0 & 54 & 0 & 10 & 1 & 0 & 0 & 81
& 0 & 7 & 0 & 0 & 0 \\ \addlinespace
\textbf{Larvae} & 12 & 0 & 9 & 0 & 0 & 0 & 32 & 0 & 0 & 0 & 0 & 0 & 41 &
0 & 0 & 0 & 0 & 0 \\ \addlinespace
\textbf{Humus} & 0 & 24 & 2 & 8 & 1 & 2 & 0 & 27 & 0 & 26 & 1 & 3 & 0 &
28 & 0 & 49 & 1 & 3 \\ \addlinespace
\textbf{Invertebrate eggs} & 15 & 0 & 10 & 3 & 0 & 0 & 33 & 0 & 2 & 5 &
0 & 0 & 52 & 0 & 1 & 4 & 0 & 0 \\ \addlinespace
\textbf{Enchytraeids} & 17 & 0 & 7 & 4 & 0 & 0 & 41 & 0 & 0 & 4 & 0 & 0
& 46 & 0 & 0 & 3 & 0 & 0 \\ \addlinespace
\textbf{Invertebrate carrion} & 5 & 22 & 2 & 6 & 1 & 2 & 9 & 30 & 0 & 28
& 1 & 3 & 11 & 31 & 0 & 40 & 1 & 4 \\ \addlinespace
\bottomrule
\end{longtable}

\newpage

>>>>

%
Víctor Nicolás\,Velazco%
%
\,\textsuperscript{1}\quad %
Carlos Eduardo\,Coviella%
%
\,\textsuperscript{1}\quad %
Liliana Beatriz\,Falco%
%
\,\textsuperscript{1}\quad %
\href{https://orcid.org/0000-0002-7911-4398}{Leonardo Ariel\,Saravia}%
%
\,\textsuperscript{2,3}

@@

\textbf{Author contributions:} LF and LS originally formulated the idea,
NV, CC developed the methodology, NV, CC, LF, and LS analyzed the data
and wrote the manuscript.

@@

@@

\scriptsize
\begin{longtable}[]{@{}lcccccccccccccccccc@{}}
\caption{Breakdown of resources by Nested boxes represent the main orders of Acari and Collembola. In parentheses is the total number of taxa for the taxonomic category. Within the cells, the number of taxa associated with the trophic resource is shown. M: Mesostigmata, S: Sarcoptiformes, T: Trombidiformes, A: Arthropleona, N: Neelipleona, Sy: Symphypleona.}\\
\toprule
\textbf{Trophic Resource} & \multicolumn{6}{l}{FAMILY} & \multicolumn{6}{l}{GENERA} & \multicolumn{6}{l}{SPECIES} \\ \addlinespace
& M & S & T & A & N & Sy & M & S & T & A & N & Sy & M & S & T & A & N &
Sy \\ \addlinespace
\midrule
\endhead
\textbf{Total} & 34 & 82 & 32 & 9 & 1 & 3 & 89 & 157 & 28 & 58 & 2 & 10
& 136 & 264 & 22 & 154 & 1 & 13 \\ \addlinespace
\textbf{Saprophytic fungi} & 7 & 68 & 10 & 9 & 1 & 2 & 11 & 120 & 10 &
54 & 1 & 7 & 7 & 160 & 3 & 119 & 1 & 8 \\ \addlinespace
\textbf{Microfauna} & 32 & 26 & 23 & 8 & 0 & 0 & 80 & 40 & 4 & 33 & 0 &
0 & 106 & 47 & 0 & 39 & 0 & 0 \\ \addlinespace
\textbf{Bacteria} & 4 & 55 & 6 & 9 & 1 & 2 & 4 & 91 & 7 & 38 & 2 & 5 & 3
& 109 & 7 & 67 & 1 & 5 \\ \addlinespace
\textbf{Litter} & 0 & 43 & 0 & 8 & 1 & 3 & 0 & 79 & 0 & 35 & 1 & 6 & 0 &
124 & 0 & 59 & 1 & 5 \\ \addlinespace
\textbf{Mycorrhizal fungi} & 2 & 31 & 3 & 7 & 0 & 1 & 1 & 44 & 0 & 28 &
0 & 2 & 0 & 54 & 0 & 46 & 0 & 2 \\ \addlinespace
\textbf{Plant tissue} & 0 & 42 & 5 & 7 & 0 & 2 & 0 & 72 & 4 & 20 & 0 & 7
& 0 & 100 & 3 & 26 & 0 & 7 \\ \addlinespace
\textbf{Springtails} & 24 & 0 & 27 & 2 & 0 & 0 & 53 & 0 & 13 & 3 & 0 & 0
& 80 & 0 & 9 & 4 & 0 & 0 \\ \addlinespace
\textbf{Mites} & 21 & 0 & 26 & 1 & 0 & 0 & 54 & 0 & 10 & 1 & 0 & 0 & 81
& 0 & 7 & 0 & 0 & 0 \\ \addlinespace
\textbf{Larvae} & 12 & 0 & 9 & 0 & 0 & 0 & 32 & 0 & 0 & 0 & 0 & 0 & 41 &
0 & 0 & 0 & 0 & 0 \\ \addlinespace
\textbf{Humus} & 0 & 24 & 2 & 8 & 1 & 2 & 0 & 27 & 0 & 26 & 1 & 3 & 0 &
28 & 0 & 49 & 1 & 3 \\ \addlinespace
\textbf{Invertebrate eggs} & 15 & 0 & 10 & 3 & 0 & 0 & 33 & 0 & 2 & 5 &
0 & 0 & 52 & 0 & 1 & 4 & 0 & 0 \\ \addlinespace
\textbf{Enchytraeids} & 17 & 0 & 7 & 4 & 0 & 0 & 41 & 0 & 0 & 4 & 0 & 0
& 46 & 0 & 0 & 3 & 0 & 0 \\ \addlinespace
\textbf{Invertebrate carrion} & 5 & 22 & 2 & 6 & 1 & 2 & 9 & 30 & 0 & 28
& 1 & 3 & 11 & 31 & 0 & 40 & 1 & 4 \\ \addlinespace
\bottomrule
\end{longtable}
\normalsize
